\textbf{Regressions And Stuff}

### 2016-09-29 paper2/paper.tex
intro to gradient descent

\documentclass[letterpaper, twocolumn,11pt]{article}
\usepackage{epsfig,endnotes,amsmath,usenix}

@@

\author{
\rm{Vahid Fazel-Rezai}\\
\rm{\texttt{vfazel@mit.edu}}
\and 
\rm{Akshay Ravikumar}\\
\rm{\texttt{akshayr@mit.edu}}
}

@@

\section{Gradient Descent}
\subsection{Batch Gradient Descent}
\subsection{Stochastic Gradient Descent}
\subsection{Effect of Finite Gradient}

>>>>

\documentclass[letterpaper, twocolumn,10pt]{article}
\usepackage{epsfig,endnotes,amsmath,usenix}

@@

\author{}

@@

\section{Gradient Descent}

\emph{Gradient descent} is an iterative optimization algorithm; in other words, it calculates the parameters $\mathbf{x}$ that minimize a given objective function $f(\mathbf{x})$. The algorithm repeatedly translates an initial \emph{guess} $\mathbf{x}_0$ in a direction proportional to the negative \emph{gradient} $\nabla f(x)$.

In every step of the itreration, we update our guess as following:
\begin{align*}
\mathbf{x}_{n+1} = \mathbf{x} - \lambda \nabla f(\mathbf{x}_{n})
\end{align*}
where $\lambda$ is the \emph{step size} of the iteration. The algorith terminates upon the following convergence condition: 
\begin{align*}
|f(\mathbf{x}_{n+1}) - f(\mathbf{x}_{n})| < \delta
\end{align*}
where $\delta$ is the convergence \emph{threshold}. Upon convergence, the algorithm returns a final guess of $\mathbf{x}_{\text{opt}} = \mathbf{x}_{n+1}$.

In this section, we compare two methods of gradient descent: \emph{batch gradient descent}, which computes a gradient over all samples for each iteration, and \emph{stochastic gradient descent}, which uses pointwise gradients instead.

To analyze the perforamnce of the different algorithms, we use the \emph{Gaussian function}:
\begin{align*}
f(x) = - \dfrac{1}{\sqrt{(2\pi)^n |\sigma|}} \exp \left[-\dfrac{1}{2} (x - u)^T \sigma^{-1} (x-u)\right]
\end{align*}
In addition, we use the \emph{quadratic bowl function}:
\begin{align*}
f(x) = \dfrac{1}{2} x^T A x - x^T b 
\end{align*}
Finally, we use the \emph{least squares error} function:
\begin{align*}
J(\theta) = |X\theta - y|^2
\end{align*}

We analyze the affects of step size ($\lambda$), threshold ($\delta$), and initial guess $\mathbf{x}_{0}$ on the performance and accuracy of the gradient descent algorithm.

\subsection{Batch Gradient Descent}

\subsection{Stochastic Gradient Descent}
\subsection{Effect of Finite Gradient}
